Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-06-17 article.tex

\section{Computing the longest $(213,231)$-avoiding subsequence}
\label{section:LCS}

	This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
	Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
	in each input permutation.
	This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$. Thus we focus on the cases where only one or two permutations are given in input.

	We start with the easiest case where we are given just one input permutation.
	We need the set of descent elements and the set of ascent elements.
	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
	$M(\pi) = \{i | \stripe{\pi}{i} = \dstep \} \cup \{n\}$.\\

@@

\begin{proof}
Consider the following problem,
that compute the longest stripe common to $\pi_1$ and $\pi_2$.
Given two permutations $\pi_1$ and $\pi_2$,\\

$$
\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
$$
\begin{center}
= $\max$ \{$|s|$ $|$ $s$ occurs in $\pi_1[i_1:]$ with every element is in $[\lb_1,\ub_1]$ and $s$ occurs in $\pi_2[i_2:]$ with every element is in $[\lb_2,\ub_2]$ \}
\end{center}

We show that we can compute by induction the problem.\\

>>>>

\section{Computing the longest $(213,231)$-avoiding pattern}
\label{section:LCS}

	This section is devoted to finding longest $(213,231)$-avoiding patterns 
	in permutations.
	We start with the easiest case where we are given just one input permutation
	and we are asked to find the longest $(213,231)$-avoiding pattern that 
	occurs in the input permutation.
	% This section is focused on a problem related to the pattern matching problem, finding the longest $(213,231)$-avoiding subsequences in permutations:
	% Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
	% in each input permutation.
	% This problem is know to be NP-Hard for an arbitrary number of permutations and we do not hope it to be solvable in polynomial time even with the constraint of the subsequence must avoid $(213,231)$. Thus we focus on the cases where only one or two permutations are given in input.

	We need the set of descent elements and the set of ascent elements.
	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
	$M(\pi) = \{i | \stripe{\pi}{i} = \dstep \} \cup \{n\}$.\\

@@

\begin{proof}
Consider the following problem
that computes the longest stripe common to $\pi_1$ and $\pi_2$:
Given two permutations $\pi_1$ and $\pi_2$, we define
$
\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
=
\max\{|s| \;|\; s \text{ occurs in } \pi_1[i_1:] \text{ with every element is in }
[\lb_1,\ub_1] \text{ and } s \text{ occurs in } \pi_2[i_2:] \text{ with every element is in }
[\lb_2,\ub_2]\}$.

We show how to solve this problem by dynamic programming.
